TBD

### 2021-02-24 outputs/paper/paper.Rmd
Update the format of tables

  kable(chi_df,
        digits = 2,
        caption = capt,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    footnote(symbol = "The Chi-squared statistic is significant at the 0.05 level") %>%
    kable_paper(c("striped", "hover"))
}
```

@@

```{r Q2, echo = FALSE, message = FALSE}
### How would you best describe the scale of your restaurant? (in terms of space and seating capacity)
### Small (full seating capacity is under 30)
### Medium (full seating capacity between 30 and 60)
### Large (full seating capacity is 60+) "
ggplot(data = all_simulated_dataset, mapping = aes (x = Q2, fill = type)) +
    geom_bar() +
  scale_x_discrete(limit = c ("Small", "Medium", "Large")) +
  labs(x = "Seating Capacity",
       y = "# of Restaurants",
       fill = "Condition",
       title = "Scale of restaurant (space/seating capacity)") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

>>>>

  kable(chi_df,
        digits = 2,
        caption = capt,
        booktabs = T,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    footnote(symbol = "The Chi-squared statistic is significant at the 0.05 level") %>%
    kable_paper(c("striped", "hover"))
}
```

@@

```{r Q2, echo = FALSE, message = FALSE}
### How would you best describe the scale of your restaurant? (in terms of space and seating capacity)
### Small (full seating capacity is under 30)
### Medium (full seating capacity between 30 and 60)
### Large (full seating capacity is 60+) "
ggplot(data = all_simulated_dataset, mapping = aes (x = Q2, fill = type)) +
    geom_bar() +
  scale_x_discrete(limit = c ("Small", "Medium", "Large")) +
  labs(x = "Seating Capacity",
       y = "# of Restaurants",
       fill = "Condition",
       title = "Scale of restaurant (space/[eseating capacity)") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```
